---
title: "Quick exploration of some basic S3 programming"
author: "Herbert Braselmann"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myfirstS3steps}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### S3 method `print.my1stClass`
Not so simple in R-devel 4.0.0? Here (2019-11-07 r77386) -- "Unsuffered Consequences" on macOS 10.15.1 Catalina, compared to R 3.5.1 

(1) A simple list `l` is defined, containing two entries `x` and `y`, and a class attribut is assigned, matching to the S3 method. Can also be numerical vectors. The default `print` function show its entries.
```{r}
l <- list(x=2, y=3)
class(l) <- "my1stClass"
print(l)
```

(2) After attaching the package, method `print.my1stClass` writes the sumproduct.
```{r}
library(myfirstS3steps)
print.my1stClass(l)
```

(3) In R <= 3.6.1 the output of `print` looks like in 2. when `l` is of class `my1stClass`. In R-devel 4.0.0 it falls back to `print.default` though the method appears in the list of S3 methods for print. It works well in R 4.0.0, when the method is sourced and appears in the global environment (not shown here).
```{r}
print(l)
.S3methods(class = "my1stClass")
```

### Session Info
```{r}
sessionInfo()
```

